XXXXX

### 2014-12-19 paper/RDF validation requirements/RDF validation requirements.tex
Aggregations
requirements evaluation complete

\newenvironment{evaluation}{
  \scriptsize
  \sffamily
  \vspace{0.3cm}
  \begin{tabular}{l|c|c|c|c|c}
  \hline
  \textbf{constraint} & \textbf{OWL2-DL} & \textbf{OWL2-QL} & \textbf{ReSh} & \textbf{ShEx} & \textbf{SPIN} \\
  \hline

@@

>>>>

\newenvironment{evaluation}{
  \scriptsize
  \sffamily
  \vspace{0.3cm}
  \begin{tabular}{l|c|c|c|c|c|c}
  \hline
  \textbf{constraint} & \textbf{DSP} & \textbf{OWL2-DL} & \textbf{OWL2-QL} & \textbf{ReSh} & \textbf{ShEx} & \textbf{SPIN} \\
  \hline

@@

\section{Aggregations}

\begin{itemize}
  \item Some constraints require aggregating multiple values, especially via COUNT, MIN and MAX. 
\end{itemize}

\begin{DL}
Not expressible in DL
\end{DL}

\section{Evaluation}

\begin{evaluation}
*Subsumption & \ding{55} & $\checkmark$ & $\checkmark$ & $\sim$ & $\checkmark$ & $\checkmark$ \\
*Class Equivalence & \ding{55} & $\checkmark$ & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ \\
*Sub Properties & \ding{55} & $\checkmark$ & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ \\
*Property Domain & \ding{55} & $\checkmark$ & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ \\
*Property Range & \ding{55} & $\checkmark$ & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ \\
*Inverse Object Properties & \ding{55} & $\checkmark$ & $\checkmark$ & $\sim$ & \ding{55} & $\checkmark$ \\
*Symmetric Object Properties & \ding{55} & $\checkmark$ & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ \\
*Asymmetric Object Properties & \ding{55} & $\checkmark$ & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ \\
*Reflexive Object Properties & \ding{55} & $\checkmark$ & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ \\
*Irreflexive Object Properties & \ding{55} & $\checkmark$ & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ \\
Disjoint Properties & \ding{55} & $\checkmark$ & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ \\
Disjoint Classes & \ding{55} & $\checkmark$ & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ \\
Context-Sp. Property Groups & \ding{55} & $\sim$ & $\sim$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
Context-Sp. Inclusive OR of P. & \ding{55} & $\sim$ & $\sim$ & \ding{55} & \ding{55} & $\checkmark$ \\
Context-Sp. Inclusive OR of P. Groups & \ding{55} & $\sim$ & $\sim$ & \ding{55} & \ding{55} & $\checkmark$ \\
Recursive Queries & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\sim$ \\
Individual Inequality & \ding{55} & $\checkmark$ & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ \\
*Equivalent Properties & \ding{55} & $\checkmark$ & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ \\
Property Assertions & \ding{55} & $\checkmark$ & $\sim$ & \ding{55} & \ding{55} & $\checkmark$ \\
Data Property Facets & \ding{55} & $\checkmark$ & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ \\
Literal Pattern Matching & \ding{55} & $\checkmark$ & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ \\
Negative Literal Pattern Matching & \ding{55} & $\checkmark$ & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ \\
*Object Property Paths & \ding{55} & $\checkmark$ & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
*Intersection & \ding{55} & $\checkmark$ & \ding{55} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
*Disjunction & \ding{55} & $\checkmark$ & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
*Negation & \ding{55} & $\checkmark$ & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
*Existential Quantification & \ding{55} & $\checkmark$ & \ding{55} & $\sim$ & $\sim$ & $\checkmark$ \\
*Universal Quantification & \ding{55} & $\checkmark$ & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
*Minimum Unqualified Cardinality & $\checkmark$ & $\checkmark$ & \ding{55} & $\sim$ & $\checkmark$ & $\checkmark$ \\
*Minimum Qualified Cardinality & $\checkmark$ & $\checkmark$ & \ding{55} & $\sim$ & $\checkmark$ & $\checkmark$ \\
*Maximum Unqualified Cardinality & $\checkmark$ & $\checkmark$ & \ding{55} & $\sim$ & $\checkmark$ & $\checkmark$ \\
*Maximum Qualified Cardinality & $\checkmark$ & $\checkmark$ & \ding{55} & $\sim$ & $\checkmark$ & $\checkmark$ \\
*Exact Unqualified Cardinality & $\checkmark$ & $\checkmark$ & \ding{55} & $\sim$ & $\checkmark$ & $\checkmark$ \\
*Exact Qualified Cardinality & $\checkmark$ & $\checkmark$ & \ding{55} & $\sim$ & $\checkmark$ & $\checkmark$ \\
*Transitive Object Properties & \ding{55} & $\checkmark$ & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
Context-Sp. Exclusive OR of P. & \ding{55} & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ & $\checkmark$ \\
Context-Sp. Exclusive OR of P. Groups & \ding{55} & $\sim$ & \ding{55} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
Allowed Values & $\checkmark$ & $\checkmark$ & \ding{55} & $\checkmark$ & $\checkmark$& $\checkmark$ \\
Not Allowed Values & \ding{55} & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ & $\checkmark$ \\
Literal Ranges & \ding{55} & $\checkmark$ & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
Negative Literal Ranges & \ding{55} & $\checkmark$ & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
Required Properties & $\checkmark$ & $\checkmark$ & \ding{55} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
Optional Properties & $\checkmark$ & $\checkmark$ & \ding{55} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
Repeatable Properties & $\checkmark$ & $\checkmark$ & \ding{55} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
Negative Property Constraints & \ding{55} & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ & $\checkmark$ \\
*Individual Equality & \ding{55} & $\checkmark$ & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
*Functional Properties & \ding{55} & $\checkmark$ & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
*Inverse-Functional Properties & \ding{55} & $\checkmark$ & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
*Value Restrictions & $\checkmark$ & $\checkmark$ & \ding{55} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
*Self Restrictions & \ding{55} & $\checkmark$ & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
Primary Key Properties & \ding{55} & $\checkmark$ & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
*Class-Specific Property Range & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
*Class-Sp. Reflexive Object P. & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
Membership in Controlled Vocabularies & $\checkmark$ & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
IRI Pattern Matching & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ & $\checkmark$ \\
Literal Value Comparison & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ & $\checkmark$ \\
Define Order & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
Validation Levels & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
String Operations & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
\end{evaluation}

\begin{evaluation}
Context-Specific Valid Classes & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
Context-Specific Valid Properties & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
Default Values & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ & \ding{55} & $\checkmark$ \\
Mathematical Operations & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
Language Tag Matching & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
Language Tag Cardinality & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
Whitespace Handling & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
HTML Handling & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
Conditional Properties & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
Recommended Properties & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
Handle RDF Collections & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
Value is Valid for Datatype & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
*Exploiting Class/Property Specialization Ontology Axioms & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
*Cardinality Shortcuts & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
Aggregations & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
\end{evaluation}
